---
always_allow_html: true
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load the package required to read JSON files.
library(rjson)
library(reticulate)
library(dplyr)
library(sentimentr)
library(lexicon)
library(magrittr)
library(stringr)

use_python("/Users/Caspar/Library/r-miniconda/envs/r-reticulate/bin/python")
```
## Load data 
```{python}
#py_install("pandas")
import pandas as pd 
import gzip

def parse(path):
  g = gzip.open(path, 'rb')
  for l in g:
    yield eval(l)

def getDF(path):
  i = 0
  df = {}
  for d in parse(path):
    df[i] = d
    i += 1
  return pd.DataFrame.from_dict(df, orient='index')

tg_review = getDF('/Users/Caspar/Downloads/reviews_Toys_and_Games_5.json.gz')


tg_review
```

## Python format to R format
```{r}
df2 <- py$tg_review
```

```{r}
tg_review_r <- df2[,c("reviewerName","reviewText","overall","summary","reviewTime")]
tg_review_r$reviewerName <- unlist(tg_review_r$reviewerName)

tg_review_r$reviewTime <- str_replace_all(tg_review_r$reviewTime,"([0-9]{2})\\s([0-9]{1,2}),\\s([0-9]{4})",
                                       "\\3-\\2-\\1")
tg_review_r$reviewTime <- str_replace_all(tg_review_r$reviewTime,"-([0-9])-", "-0\\1-")

                                          
tg_review_r$reviewTime  <- str_replace_all(tg_review_r$reviewTime,"([0-9]{4})-([0-9]{2})-([0-9]{2})",
                                       "\\1-\\3-\\2")
```

## Board Games dataset
```{r}
matches<- str_detect(tg_review_r$reviewText,"[Bb]oard.?")

board_game_df <- tg_review_r[which(matches),]

```

## Text Cleaning
```{r}
library(stringr)
library(tidyr)

boardGames_review <- board_game_df

boardGames_review$reviewText <- str_to_lower(boardGames_review$reviewText)

head(boardGames_review$reviewText)

```

### Stem text
```{r}
library(tm)

stem_bg <- tm::stemDocument(boardGames_review$reviewText)

documentsCorp <- tm::SimpleCorpus(VectorSource(stem_bg))

documentsDTM <- DocumentTermMatrix(documentsCorp)

inspect(documentsDTM)
```

### lemmatize text
```{r}
library(textstem)
boardGames_review$reviewText <- lemmatize_strings(boardGames_review$reviewText)
```

### sentiment analysis 
```{r}
library(sentimentr)
jocker_bg <- sentiment(get_sentences(boardGames_review$reviewText[1:200]), polarity_dt = lexicon::hash_sentiment_jockers)

jocker_bg_summary <- jocker_bg%>%
  group_by(element_id)%>%      
  summarize(meanSentiment =mean(sentiment))
```

```{r}
boardGames_review$element_id = 1:nrow(boardGames_review)

boardGames_review_sub200 <- left_join(boardGames_review[1:200,], jocker_bg_summary, by = "element_id")

boardGames_review_sub200 <- boardGames_review_sub200[order(-boardGames_review_sub200$meanSentiment),] 

head(boardGames_review_sub200$reviewText)
  
```

## Topic Models

```{r}
library(stm)

set.seed(1001)

holdoutRows <- sample(1:nrow(boardGames_review), 100, replace = FALSE)

reviewText <- textProcessor(documents = boardGames_review$reviewText[-c(holdoutRows)], 
                          metadata = boardGames_review[-c(holdoutRows), ], 
                          stem = FALSE)

reviewPrep <- prepDocuments(documents = reviewText$documents, 
                               vocab = reviewText$vocab,
                               meta = reviewText$meta)
```

```{r}
kTest <- searchK(documents = reviewPrep$documents, 
             vocab = reviewPrep$vocab, 
             K = c(3,4,5,10), verbose = FALSE)   # K = c(3, 4, 5, 10, 20)

plot(kTest)
```

Looks like four topics are the best choice
```{r}
topics4 <- stm(documents = reviewPrep$documents, 
             vocab = reviewPrep$vocab, seed = 1001,
             K = 4, verbose = FALSE)
```

```{r}
plot(topics4)
```

```{r}
labelTopics(topics4)
```

```{r}
thoughts_4 <- findThoughts(topics4, texts = reviewPrep$meta$reviewText, n = 1)
```


```{r}
head(topics4$theta, 15)
```

We found that Doc 14 has a probability of 81.6% for belonging to topic 5 and let's pull the original review out and see
 
```{r}
board_game_df[14,'reviewText']
```

```{r}
tail(topics4$theta, 15)
```

Doc 8913 has a probability of 84.1% for belonging to topic 1
 
```{r}
board_game_df[8913,'reviewText']
```

```{r}
reviewPrep$meta[14, ]

reviewPrep$meta[8913, ]
```

We can also see what terms are in documents 14:
```{r}
reviewPrep$documents[[14]]
```

```{r}
reviewPrep$vocab[reviewPrep$documents[[14]][1, ]]
```

```{r}
reviewPrep$vocab[reviewPrep$documents[[8913]][1, ]]
```

## Prediction sentiment scores for holdout samples 
```{r}
newReviewText <- textProcessor(documents = boardGames_review$reviewText[holdoutRows], 
                          metadata = boardGames_review[holdoutRows, ], 
                          stem = FALSE)

newReviewCorp <- alignCorpus(new = newReviewText, old.vocab = topics4$vocab)

newReviewFitted <- fitNewDocuments(model = topics4, documents = newReviewCorp$documents, 
                newData = newReviewCorp$meta, origData = reviewPrep$meta)


newReviewFitted$theta[1:10,]

```

```{r}
clean_boardGames_review <- boardGames_review%>%
  mutate( 
         reviewText = str_replace_all(reviewText, "\n", " "),   
         reviewText = str_replace_all(reviewText, "(\\[.*?\\])", ""),
         reviewText = str_squish(reviewText), 
         reviewText = gsub("([a-z])([A-Z])", "\\1 \\2", reviewText), 
         reviewText = tolower(reviewText), 
         reviewText = removeWords(reviewText, c("’", stopwords(kind = "en"))), 
         reviewText = removePunctuation(reviewText), 
         reviewText = removeNumbers(reviewText),
         reviewText = textstem::lemmatize_strings(reviewText), 
         year = lubridate::year(reviewTime))
```


```{r}
predictorText <- textProcessor(documents = clean_boardGames_review$reviewText, 
                          metadata = clean_boardGames_review, 
                          stem = FALSE)

reviewPrep <- prepDocuments(documents = predictorText$documents, 
                               vocab = predictorText$vocab,
                               meta = predictorText$meta)

topicPredictor <- stm(documents = reviewPrep$documents,
             vocab = reviewPrep$vocab, prevalence = ~ year,
             data = reviewPrep$meta, K = 4, verbose = FALSE)


yearEffect <- estimateEffect(1:4 ~ year, stmobj = topicPredictor,
               metadata = reviewPrep$meta)

summary(yearEffect, topics = c(1:4))

plot.estimateEffect(yearEffect, "year", method = "continuous",
                    model = topicPredictor, topics = 1, labeltype = "frex")

plot.estimateEffect(yearEffect, "year", method = "continuous",
                    model = topicPredictor, topics = 2, labeltype = "frex")

plot.estimateEffect(yearEffect, "year", method = "continuous",
                    model = topicPredictor, topics = 3, labeltype = "frex")

plot.estimateEffect(yearEffect, "year", method = "continuous",
                    model = topicPredictor, topics = 4, labeltype = "frex")
```

